# Publication quality figures

A picture is worth a thousand words. Let's create some figures.

Objectives:

* To be able to use `ggplot2` to generate publication quality graphics of
  scatter and line plots
* To understand the basic grammar of graphics, including the aesthetics
  and geometry layers, adding statistics, transforming scales, and
  colouring or panelling by groups


http://swcarpentry.github.io/r-novice-gapminder/08-plot-ggplot2/


Trend line for each continent, not that useful but makes the point:

```{r}
ggplot(data = gapminder,
       aes(x=gdpPercap,
           y=lifeExp,
           size=pop,
           shape=continent,
           color=country,
           group=continent)) +
geom_point(alpha=0.5) + scale_x_log10() +
geom_smooth(method='lm', aes(colour=continent)) +
theme(legend.position = 'none')
```
This works because:
```{r}
ggplot(data=gapminder[gapminder$continent=='Europe',],
       aes(x=gdpPercap,
           y=lifeExp,
           size=pop,
           shape=continent,
           color=country,
           group=continent)) +
geom_point(alpha=0.5) +
scale_x_log10() +
geom_smooth(method='lm', aes(colour=continent)) +
theme(legend.position = 'none')
```
